### 2014-03-16 HowtoHowtoCapon/submission/submit1/answer/answer.tex
Calling it a night

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as to the best of our knowledge this term is usually used to describe the use of subarrays to reduce complexity, while we average over subarrays to deal with the coherent echoes present in \emph{active} systems. We still apply the weights to the full array. To avoid confusion we have now stated this better up front in the article.}

@@

\ai{Yes, the initial plots had the total GPU processing time included. But since there are three versions of the covariance building step, there TODO }

>>>>

\ai{You are right that subarray averaging is important in our study. But we believe that "subarray MVDR" would be misleading, as to the best of our knowledge this term is usually used to describe the use of subarrays to reduce complexity, while we average over subarrays to deal with the coherent echoes present in \emph{active} systems. We still apply the weights to the full array. To avoid confusion we have now stated this better up front in the article (section I paragraph 5).}

@@

\ai{The reviewer has a point. But since there are 3 occurrences of the covariance processing time, including the total time GPU processing time would introduce three new lines. We feel this would clutter the plot unnecessarily as it is not too hard to derive the total time by looking at the current plots. Putting the total processing time in the MATLAB/C total time figure is an option, but then a logarithmic y-scale would necessary and detail would be lost.}
